### 2021-05-12 analysis/statistical_analyses.Rmd
made pass through statistical_analyses notebook

@@

# Experiment 1 data frame 
d1 <- read_csv(dpath_exp1) #%>%
d2 <- read_csv(dpath_exp2) #%>%

@@

### Plot data

@@

### Stats for Expt 1

@@

# For simplicity run analyses on dual networks only

@@

### Fig 2
```{r exp2plot, include=TRUE, fig.height=4, fig.width=6}

>>>>

This notebook uses `brms` to analyze data from the two experiments reported in Fermo, A. & Kemp, C. (2021). Temporal Continuity and the Judgment of Actual Causation.

@@

# Experiment 1 data frame 
d1 <- read_csv(dpath_exp1) 
d2 <- read_csv(dpath_exp2)

@@

### Plot Experiment 1 Data

@@

### Statistical analyses for Expt 1

@@

# the state_or_event variable doesn't apply to chains, so for simplicity we run analyses on dual networks only

@@

### Plot Experiment 2 data

```{r exp2plot, include=TRUE, fig.height=4, fig.width=6}
